Assignment 5

### 2015-02-25 rmtw/a5/latex8.tex
fds

The method we shall use to attempt to answer our research questions is a Systematic Literature Review (SLR) \cite{keele2007guidelines}. An SLR is the most appropriate research methodology for two main reasons, we wish to summarise the existing evidence of when MDSD is applicable in industry and to fill gaps in literature for examples of when MDSD is not applicable \cite{keele2007guidelines}. For these same reasons, other methodology techniques are not as applicable. For example, a quantitative study is not appropriate as we are not trying to prove, disprove or generalise a hypothesis. A qualitative study would be useful if we were interested in exploring a hypothesis and for similar reasons a case study would not be applicable as we are not concerning ourselves with how MDSD works in a real setting. Likewise, as industry and academia seem to differ, it implies that there can be bias in both camps. By performing an SLR we help to alleviate some of this bias but we do not eliminate it entirely \cite{keele2007guidelines}.

It's important to note that we will not be performing either a Systematic Mapping Study nor a Tertiary Review of existing literature. There is sufficient evidence in existence for the applicability of MDSD such that we can rule out the need to perform a Systematic Mapping Study. Furthermore, there insufficient SLRs that have been conducted thus a Tertiary Review is not possible nor appropriate at this time.

>>>>

The method we shall use to attempt to answer our research questions is a Systematic Literature Review (SLR) \cite{keele2007guidelines}. An SLR is the most appropriate research methodology for two main reasons, we wish to summarise the existing evidence of when MDSD is applicable in industry and to fill gaps in literature for examples of when MDSD is not applicable \cite{keele2007guidelines}. For these same reasons, other methodology techniques are not as applicable. For example, a quantitative study is not appropriate as we are not trying to prove, disprove or generalise a hypothesis. A qualitative study would be useful if we were interested in exploring a hypothesis and for similar reasons a case study would not be applicable as we are not concerning ourselves with how MDSD works in a real setting. Likewise, as industry and academia seem to differ in opinion, it implies that there can be bias in both XXX camps. By performing an SLR we help to alleviate some of this bias but we do not eliminate it entirely \cite{keele2007guidelines}.

It is important to note that we will not be performing either a Systematic Mapping Study nor a Tertiary Review of existing literature. There is sufficient evidence in existence for the applicability of MDSD such that we can rule out the need to perform a Systematic Mapping Study. Furthermore, there insufficient SLRs that have been conducted thus a Tertiary Review is not possible nor appropriate at this time.
